The pollination trade-off

### 2019-03-06 paper/manuscript.Rmd
Format table of random effects AIC selection in supp info
Finish off text edits for second subsection of results

We tested two structures for the random effects. 
As determined by AICc, the random structure best supported by the data was the one that fit an intercept for each species in each community (as opposed to a common intercept for each species irrespective of the community they belong to). 
This structure was best for both the models of conspecific and heterospecific pollen (Table SXX).

Out of the four variables we explored, we found that the plants' mean visit effectiveness and its abundance were the most important ecological variables predicting pollen deposition in plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a). 
Surprisingly, the number of shared pollinators was comparatively unimportant, particularly for models of heterospecific pollen deposition, as it was only included in models with relatively large AICc values.

We found that the relationship between each of the strategies and pollen deposition was similar for both conspecific and heterospecific pollen. 
This is, strategies that were associated with an increase (or a decrease) in conspecific pollen, were also associated with an increase (or a decrease) in heterospecific pollen deposition. 
Specifically, the plants' mean visit effectiveness had a positive effect on pollen deposition (Figure \@ref(fig:fig-average-qual-quant)b). 
The positive association with conspecific pollen indicates a positive effect on the quantity of pollination. 
However, the mean of the coefficients that relates visit effectiveness to heterospecific pollen deposition is slightly larger than that of conspecific pollen. 
This suggest a negative, albeit marginal, relationship of visit effectiveness and our definition of the quality of the pollination service (Figure \@ref(fig:fig-average-qual-quant)c). 
Contrastingly, the plants' relative abundance had a negative effect in pollen deposition (and consequently the quantity of pollination), but the difference between the coefficients in the models of conspecific and heterospecific pollen indicates a considerable positive impact on the quality of pollination. 
The third most important variable, functional originality, had a positive, although comparatively smaller, association with both the quantity and quality of pollination. 
Finally, the number of shared pollinators had a negative association with the quantity and quality of pollination, but these impacts were small when compared to the other variables. 
Although relative abundance, the number of shared pollinators, and the visit effectiveness were positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect that each of them had on conspecific pollen was relatively similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)).

@@

>>>>

We tested two structures for the random effects. 
As determined by AICc, the random structure best supported by the data was the one that fit an intercept for each species in each community (as opposed to a common intercept for each species irrespective of the community they belong to). 
This structure was best for both the models of conspecific and heterospecific pollen (Table \@ref(S-tab:table-aic-random-models)).

Of the four variables we considered, we found that a plant's mean visit effectiveness and abundance were the most important ecological variables predicting pollen deposition in plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a). 
Surprisingly, the number of shared pollinators was comparatively unimportant, particularly for models of heterospecific pollen deposition, as it was only ever included in models with relatively large AICc values.

@@

We found that the relationship between each of the ecological factors and pollen deposition was similar for both conspecific and heterospecific pollen. 
That is, strategies that were associated with an increase in conspecific pollen were also associated with an increase in heterospecific pollen deposition. 
Specifically, the plants' mean visit effectiveness had a positive effect on pollen deposition (Figure \@ref(fig:fig-average-qual-quant)b). 
However, the effect size was slightly larger for heterospecific than for conspecific pollen. 
This indicates that, although there is a positive association between visit effectiveness and the *absolute* amount of conspecific pollen, there is a negative relationship with the *relative* amount of conspecific relative to heterospecific pollen (Figure \@ref(fig:fig-average-qual-quant)c). 
In contrast, a plants' relative abundance had a negative effect on the absolute amount of conspecific pollen, but the mean difference between the coefficients in the models indicates a positive association with the relatvie amount of conspecific pollen (Figure \@ref(fig:fig-average-qual-quant)c). 
The third most important variable, functional originality, had a positive, although comparatively smaller, association with both the absolute and relative amount of conspecific pollen deposited. 
Finally, the number of shared pollinators had a negative association with both the absolute and relative amounts of conspecific pollen deposited, but these impacts were small when compared to the other variables. 
Although relative abundance, the number of shared pollinators, and the visit effectiveness were all positively correlated (Figure \@ref(S-fig:fig-correlation)), the effect each had on conspecific pollen was relatively similar among models that included all or just some of these three explanatory variables (Figure \@ref(S-fig:fig-model-results)), indicating that collinearity did not influence our findings qualitatively.
